---
title: "MDE-Based Calculator"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    css: styles-with-nav.css
    vertical_layout: scroll
    logo: logo-sm.png
    favicon: favicon.png
    fig_height: 1
    navbar: 
      - { title: "Planning: MDE-Based Calculator", href: "https://sdidev.shinyapps.io/sample-size-calc-with-nav/" }
      - { title: "Planning: Runtime-Based Calculator", href: "https://sdidev.shinyapps.io/sample-size-calc-runtime-with-nav/" }
      - { title: "Planning: Sequential Test Calculator", href: "https://sdidev.shinyapps.io/sequential-test-calculator/" }
      - { title: "Analysis: Test Results Assessment", href: "https://sdidev.shinyapps.io/ABTestAnalysis/" }
      - { title: "Simulator: A/B Test Results", href: "https://sdidev.shinyapps.io/test-result-simulator/" }
    includes:
      after_body: tracking.html

runtime: shiny
---

```{r setup}
library(ggplot2)
library(dplyr)
library(purrr)
library(RColorBrewer)
library(scales)
library(rvg)       # For interactive / tooltips
library(ggiraph)   # For interactive / tooltips

```

<script>
$('.navbar-logo').wrap('<a href="https://www.searchdiscovery.com/how-we-help/services/optimization/" target=_blank>');
</script>

<div style = "margin-top: 75px">
Enter values below to calculate the number of visitors needed for each variation in an A/B test to reliably detect the desired conversion rate lift.
</div>

Row
-----------------------------

### 1. Baseline Conversion Rate and Estimated Lift %

Enter the **baseline conversion rate** for the page, experience, and audience you hope to impact (e.g., enter "5" for "5%"):

```{r}
# Baseline conversion rate
div(style="text-align: center;",
    div(style="display:inline-block;", numericInput("baseline", label = NULL, value = NA, width = "100px")),
    div(style="display:inline-block; padding-left: 5px; font-weight: bold", "%"))
```

Enter the **estimated lift percentage** you would need to see in order to make a decision (positive or negative):

```{r}
# Minimal detectable effect
div(style="text-align: center;",
    div(style="display:inline-block;", numericInput("min_effect", label = NULL, value = NA, width = "100px")),
    div(style="display:inline-block; padding-left: 5px; font-weight: bold", "%"))
```

```{r liftmessage}
# We're starting with no values for the baseline and MDE, so we want to clearly prompt
# the user to enter those and, once entered, reiterate the interpretation of those values.
# And, to wrinkle things up a bit more, we need to calculate the MDE in both directions
# if the user selects a two-tailed test.
output$liftmessage <- renderUI({
  if(is.na(input$baseline) | input$baseline == 0 |
     is.na(input$min_effect) | input$min_effect == 0){
    message <- HTML("<div style=\"color:red;\">Enter a baseline conversion rate and an estimated lift % above.</div>")
  } else {
    
    # Calculate the different values. We'll go ahead and calculate the second p2,
    # which is only needed if it's a two-tailed test. But, the if() statement will
    # decide whether to use that or not.
    baseline <- paste0(input$baseline,"%")
    p2_val_1 <- paste0(input$baseline * (1 + input$min_effect/100), "%")
    p2_val_2 <- paste0(input$baseline * (1 - input$min_effect/100), "%")
    
    # Build the actual string
    if(input$tail == "one.sided"){
      message = HTML("<div style=\"font-style: italic;\">This means you're looking to detect a change in the ",
                     "conversion rate from <strong>", baseline, "</strong> to <strong>", 
                     p2_val_1, "</strong>.</div>")
    } else {
      message = HTML("<div style=\"font-style: italic;\">This means you're looking to detect a change in the ",
                     "conversion rate from <strong>", baseline, "</strong> to <strong>", 
                     p2_val_1, "</strong> OR from <strong>", baseline, "</strong> to <strong>",
                     p2_val_2, "</strong> (as a two-tailed test).</div>")
    }
  }
})
```

_`r htmlOutput("liftmessage", inline = TRUE)`_

### 2. Traffic Volume and # of Variations

How many visit(or)s do you get to the experience, on average, **over the course of 30 days**?

```{r}
# 30-day visit(or)s
numericInput("avg_traffic", 
             label = NULL, value = NA,
             width = "150px")
```

How many total variations are you testing, including the control (e.g., a standard A/B test would be "2")?

```{r}
# of variations
numericInput("variations",
             label = NULL, value = 2,
             width = "100px")

```

Row {.tabset} 
-----------------------------

### 3. Select 1-Tailed vs. 2-Tailed

Is your hypothesis _directional_ (e.g., you expect the conversion rate to increase) or non-directional (e.g., you expect the challenger to be different, but you have no evidence to support the challenger as _better_)?

```{r}
# One-tailed or two-tailed
radioButtons("tail", label = NULL,
             choices = list("My hypothesis is directional and I want to test if B is BETTER than A (1-tailed)" = "one.sided", 
                            "My hypothesis is non-directional and I want to test if B is DIFFERENT than A (2-tailed)" = "two.sided"), 
             selected = "one.sided")
```

_Note: Results within your testing tool may vary if you select one-tailed and your testing tool uses two-tailed and vice versa._ 

**Reference:** [Differences Between a One-Tailed and a Two-Tailed Test](https://www.sciencedirect.com/science/article/pii/S0148296312000550)

### 4. Select Confidence ($1 - \alpha$)

How important is it that you do not _**erroneously report a difference**_ when, in reality, the variations are the same?

```{r}
# Confidence
div(style="display: inline-block; vertical-align:top; width: 350px",
    sliderInput(inputId = "confidence",
                label = div(style='width:300px;',
                            div(style='float:left;', 'Not Important'),
                            div(style='float:right;', 'Very Important')),
                min = 50, max = 99, value = 95, width = '300px', post = "%"))

# Checkbox to enable FWER correction for the sample size
div(style="display: inline-block;vertical-align:bottom;",
    conditionalPanel(
      condition = ("input.variations > 2"),
      checkboxInput("fwer", label = paste("Adjust sample size for family-wise error rate (FWER) using",
                                          "Bonferroni correction. This only changes results when working with more than",
                                          "two total variations."), value = TRUE)
    )
)

```

This is the **statistical confidence**. The higher you set the statistical confidence, the _less likely_ the statistical results will return a _false difference_ (aka, a false positive or a Type I error).

### 5. Select Power ($1 - \beta$)

How important is it that you do not _**erroneously report NO difference**_ when, in reality, there *is* a difference between the variations?

```{r}
# Statistical Power
sliderInput(inputId = "power",
            label = div(style='width:300px;',
                        div(style='float:left;', 'Not Important'),
                        div(style='float:right;', 'Very Important')),
            min = 50, max = 99, value = 80, width = "300px", post = "%")
```

The _higher_ you set the statistical power, the greater your likelihood of detecting a real difference if one exists and the less likely you will return a false “no difference” (aka, a false negative or a Type II error).`r tags$span(style="color:red; font-style:italic;", textOutput("power_msg", inline = TRUE))`

Row
-----------------------------

### Sample Size

The **number of visit(or)s** should be at least:

```{r output}
h1(textOutput("sample_size", inline=TRUE), span(style="display: inline-block; font-size:20px;", "per variation"))
h2(style = "text-align: center;", textOutput("total_visitors", inline=TRUE))

em(htmlOutput("range_message", inline = TRUE))

# Output a hidden field with the test duration so that a tag manager can
# grab the value and push it into analytics
tags$span(style="visibility:hidden", textOutput("duration"))
```

### Selected Test Type, Confidence, and Power

```{r selections}
h3("Test Type:", strong(textOutput("tail", inline = TRUE)))
h3("Confidence:", strong(textOutput("confidence", inline = TRUE),"%"))
h3("Power:", strong(textOutput("power", inline = TRUE),"%"))
```

The impact of these values values is reflected in the diagram below. The gray dotted line reflects a coin toss (statistical power = 50% and statistical confidence = 50%).

```{r calculations}
# Return each of the input values so they can be re-displayed. We have to repeat some
# of these because we're outputting them multiple times.
output$baseline <- renderText(paste0(input$baseline,"%"))

# This one gets embedded in a paragraph in a parenthetical, and we want it to just
# disappear if there is no value yet.
output$baseline2 <- renderText({
  if(is.na(input$baseline) | input$baseline == 0){
    output_value <- ""
  } else {
    output_value <- paste0(" (",input$baseline,"%)")
  }
})

# Back to simpleer ones
output$power <- renderText(input$power)
output$confidence <- renderText(input$confidence)
output$tail <- renderText(ifelse(input$tail == "one.sided", "One-tailed", "Two-tailed"))

# Create a warning message if Power is set below 80%
output$power_msg <- renderText(ifelse(input$power < 80,
                                      paste0("CAUTION: We recommend a minimum 80%. Statistical ",
                                             "power is the likelihood that you will be able to ",
                                             "detect an effect when an effect exists."),
                                      ""))

# Create the couple of messages that make it clear as to what ranges are being tested.
# If it's one-tailed, it's just in one direction. If it's two-tailed, then it's in two (duh).
# This is fairly repetitive with code earlier, but the message is slightly different, and
# I couldn't figure out a clean way to re-use thes ame setup.
output$range_message <- renderUI({
  
  # If a baseline and MDE aren't entered yet, then return a prompt as such
  if(is.na(input$baseline) | input$baseline == 0 |
     is.na(input$min_effect) | input$min_effect == 0){
    message <- HTML("<div style=\"color:red;\">Enter a baseline conversion rate and an estimated lift % above.</font>")
  } else {
    
    # Calculate the different values. We'll go ahead and calculate the second p2,
    # which is only needed if it's a two-tailed test. But, the if() statement will
    # decide whether to use that or not.
    baseline <- paste0(input$baseline,"%")
    p2_val_1 <- paste0(input$baseline * (1 + input$min_effect/100), "%")
    p2_val_2 <- paste0(input$baseline * (1 - input$min_effect/100), "%")
    
    # Build the actual string
    if(input$tail == "one.sided"){
      message = paste0("This is the number of visitors required to detect a change in the ",
                       "conversion rate from <strong>", baseline, "</strong> to <strong>", p2_val_1,
                       "</strong>.")
    } else {
      message = paste0("This is the number of visitors required to detect a change in the ",
                       "conversion rate from <strong>", baseline, "</strong> to <strong>", p2_val_1,
                       "</strong> OR from <strong>", baseline, "</strong> to <strong>",
                       p2_val_2, "</strong> (in a two-tailed test).")
    }
  }
  
  # Return the message.
  HTML(message)
})

# Reactive function to adjust the significance level to use 
# Bonferroni correction - FWER - if selected
sig_level <- reactive({
  if(input$fwer == TRUE){
    alpha <- (100 - input$confidence) / (100 * (input$variations - 1))
  } else {
    alpha <-  (100 - input$confidence)/100
  }
})

# Reactive function to do the actual sample size calculation. This has error
# checking baked in. And, it returns a number or a string
calc_results <- reactive({
  tryCatch(
    {
      # Calculate the result
      calc_n <- power.prop.test(p1 = input$baseline/100,
                                p2 = (input$baseline/100) * (1 + input$min_effect/100),
                                sig.level = sig_level(),
                                power = input$power/100,
                                alternative = input$tail)
      
      # Extract the sample size from the returned list and return it
      return(calc_n$n)
    },
    error = function(e){
      return("N/A")
    }
  )
})


# Calculate the sample size
output$sample_size <- renderText({
  
  # Set a value for when the # of observations is so low that they might as well
  # just flip a coin
  coin_flip_message <- "0 (Just Flip a Coin!)"
  
  # Do some checks to cover the corner cases with different messaging
  if(input$power == 50 & input$confidence == 50){
    results <- coin_flip_message
  } else {
    results <- calc_results()  # Get the results. 
    
    # Check if the results returned N/A
    if(results == "N/A"){
      results <- results   # Just pass through "N/A"
    } else {
      # Check to see if things landed such that we still rounded to 0
      if(results == 0){
        results <- coin_flip_message
      } else {
        # Return... a nice number if that's what we've got
        results <- format(round(results), big.mark=",", scientific = FALSE)
      }
    }
  }
  
  # Return the results
  results
})

# Calculate the total visitors required -- just the # per variation times
# the number of variations
output$total_visitors <- renderText({
  
  results <- calc_results()  # Get the results. 
  if((input$power == 50 & input$confidence == 50) |
     results == "N/A" | results == 0 ){
    results <- ""
  } else {
    results <-  paste0("(",
                       format(round(results * input$variations), big.mark=",", scientific = FALSE),
                       " total visitors)")
  }
})


```

Row  {data-height=400}
-----------------------------

### Runtime Based on Lift %

```{r}

# Output the time vs. minimal effect chart
plotOutput("mineffect_time")

# Calculate the values and build the chart
output$mineffect_time <- renderPlot({
  
  req(input$baseline > 0)
  req(input$avg_traffic > 0)
  req(input$variations >= 2)
  req(input$avg_traffic >= 300)   # This would be 10 visit(ors) a day.
  
  # Function to calculate the minimum effect. This is, really, calculating
  # "p2" -- the second probabiliy -- given the other various inputs. The wrinkle
  # is that power.prop.test, if only given p1, assumes p2 is *higher*. So, in
  # cases where the entered MDE is negative, we want to use "p2" for p1. This
  # only matters for one-tailed tests, actually, but there's no harm in it
  # being the case for two-tailed.
  calc_min_effect <- function(days_running){
    
    # Calculate the number of observations per group.
    n <-  round(days_running * input$avg_traffic / 30 / input$variations,0)
    
    # Set p1 as the baseline if the MDE entered is positive, and as the
    # baseline minus the minimum effect if the MDE is negative
    p1 <- ifelse(input$min_effect > 0,
                 input$baseline/100,
                 input$baseline/100 * (1 + input$min_effect/100))
    
    # Run the test to get the results.
    calc_results <- power.prop.test(n = n,
                                    p1 = p1,
                                    sig.level = sig_level(),
                                    power = input$power/100,
                                    alternative = input$tail)
    
    # Create a data frame that has the # of days run, the minimal positive lift
    # detectable, and the negative minimal effect detectable. "positive" is a bit
    # of a misnomer: if the MDE entered is negative, then this is actually a 
    # negative number
    result <- data.frame(days = days_running,
                         lift_pos = ifelse(input$min_effect > 0, 
                                           calc_results$p2/calc_results$p1 - 1,
                                           (calc_results$p2/calc_results$p1 - 1) * -1)) %>%
      # If one-tailed, set the base to be zero; otherwise, set it to be the
      # negative of lift_pos.
      mutate(lift_neg = ifelse(input$tail == "one.sided", 0, -1*lift_pos))
  }
  
  # Create a data frame with "days" of 1 to 30 and then the minimal
  # detectable affect for each day
  min_by_day <- map_dfr(seq(1:30), calc_min_effect)
  
  # Hold on to your socks. We're going to find the first day that is *above*
  # the minimum effect. This will tell us how many days we can expect to need
  # to run the test to detect the minimal lift desired.
  days_needed <- which.min(ifelse(
    (input$min_effect > 0 & min_by_day$lift_pos > input$min_effect/100) |
      (input$min_effect < 0 & min_by_day$lift_pos < input$min_effect/100),
    NA,
    abs(min_by_day$lift_pos-input$min_effect/100)))
  
  # Set the days needed as an output. We'll drop this into an hidden
  # field so that a tag manager can grab it and push it into analytics.
  output$duration <- renderText({
    if(length(days_needed) == 0){
      duration_message <- "Over 30 Days"
    } else {
      duration_message <-  as.character(days_needed)
    }
    duration_message
  })
  
  # If the minimum effect can't be hit in 30 days, we don't want to show a
  # line, and we want a message to that effect. So, set a few values to be
  # used in the relevant geoms to make the line disappear (size = 0) and to
  # set the text description.
  if(length(days_needed) == 0){
    duration_msg <-  "Over 30 Days"    # Set the message in the center
    days_needed_x_intercept <- 15                   # Set the message in the center
    days_text_hjust <-  0.5
    days_size <-  0
    days_text_val <-  "The test would take\nmore than 30 days."
    days_text_nudge <- 0
  } else {
    days_size = 1
    days_text_val = paste0(days_needed, " Days")
    days_needed_x_intercept <- days_needed
    
    # If the days is less than 25, we want to put the text on the left
    # side of the line. Otherwise, we want it on the right side.
    if(days_needed < 25){
      days_text_hjust <-  0
      days_text_nudge <-  0.5
    } else {
      days_text_hjust <-  1
      days_text_nudge <-  -0.5
    }
  }
  
  # And, more fun. Make a data frame that has all of the "minimum effect"
  # stuff. That will be a one-row data frame for a one-tailed test and
  # a two-row data frame for a two-tailed test.
  if(input$tail == "one.sided"){
    min_effect_df <- data.frame(xintercept <- days_needed_x_intercept,
                                yintercept = input$min_effect/100,
                                label = paste0(input$min_effect, "%"))
  } else {
    min_effect_df <- data.frame(xintercept <- days_needed_x_intercept,
                                yintercept = c(input$min_effect/100, -1*input$min_effect/100),
                                label = c(paste0(input$min_effect, "%"), 
                                          paste0(-1*input$min_effect, "%")))
  }
  
  # Finally, we're going to need to nudge the labels for the MDE line(s).
  # The degree to nudge them changes whether the MDE is positive or negative
  nudge_y <- ifelse(input$min_effect > 0,
                    min_by_day$lift_pos[20] - min_by_day$lift_pos[30],
                    min_by_day$lift_pos[30] - min_by_day$lift_pos[20])
  
  # Plot it!
  ggplot(data = min_by_day) +
    
    # Draw the shaded band
    geom_ribbon(mapping = aes(x = days, ymin = lift_neg, ymax = lift_pos),
                alpha = 0.1) +
    
    # Draw the x-axis and y-axis
    geom_hline(aes(yintercept = 0), colour = "gray10") +
    geom_vline(aes(xintercept = 0)) +
    
    # Draw the minimum effect line(s)
    geom_hline(data = min_effect_df,
               mapping = aes(yintercept = yintercept), colour = "#416fba",
               size = 1, linetype = "dashed") +
    
    
    # Add a text label to the minimum effect line(s)
    geom_text(data = min_effect_df,
              mapping = aes(x = 30, y = yintercept,
                            label = label),
              vjust = 0, hjust = 1, fontface = "bold", colour = "#416fba",
              nudge_y = nudge_y,
              size = 4.5) +
    
    # Draw the "days needed" line and text
    geom_vline(aes(xintercept = days_needed_x_intercept), colour = "#416fba",
               size = days_size, linetype = "dashed") +
    geom_text(data = data.frame(dummy = NA),
              mapping = aes(x = days_needed_x_intercept, y = min_by_day$lift_pos[2],
                            label = days_text_val),
              hjust = days_text_hjust, fontface = "bold", colour = "#416fba",
              nudge_x = days_text_nudge, size = 4.5) +
    
    # Draw the intersection point(s)
    geom_point(data = min_effect_df,
               aes(x = xintercept, y = yintercept),
               size = 2 * days_size,
               colour = "gray30") +
    
    labs(x = "Test Duration (Days)", y = "Lift % (Relative)") +
    scale_y_continuous(expand = c(0,0), labels = percent) +
    scale_x_continuous(expand = c(0,0), limits = c(0,31)) +
    theme_light() +
    theme(text = element_text(size = 14),
          panel.border = element_blank(),
          axis.line.y = element_blank(),
          panel.grid.minor = element_blank(),
          axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))
})
```

### Error Risk Visualization

```{r error-grid}
ggiraphOutput("error_matrix")

# Define theme
error_theme <- theme_light() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title = element_text(size = 16, face = "bold"),
        panel.grid = element_blank(),
        panel.spacing = unit(0, "lines"),
        panel.background = element_blank(),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(colour = "black", size = 14),
        legend.position = "none")

# Build the plot
output$error_matrix <- renderggiraph({
  
  # We *could* display this even without data, but we're going to blank it
  # out until values are entered.
  req(input$baseline > 0)
  req(input$min_effect > 0 | input$min_effect < 0)
  req(input$avg_traffic > 0)
  req(input$variations >= 2)
  
  # Set up a data frame to display the 2x2 matrix. For each of the columns --
  # created as vectors -- the values are: top left (true positive), top right
  # (false positive), bottom left (false negative), and bottom right (true
  # negative). If you need to decode what's going on, you just have to figure
  # out which quadrant (facet) for which the value is used. The "(100*x)^0.5"
  # is because we're using areas to represent percentages. So, we've got to
  # do some square rooting.
  error_df <- data.frame(reality = factor(c("DIFFERENCE", "NO DIFFERENCE", 
                                            "DIFFERENCE", "NO DIFFERENCE"),
                                          levels = c("DIFFERENCE", "NO DIFFERENCE")),
                         result = factor(c("DIFFERENCE", "DIFFERENCE", 
                                           "NO DIFFERENCE", "NO DIFFERENCE"),
                                         levels = c("DIFFERENCE", "NO DIFFERENCE")),
                         label = c(paste0("True Difference\n", input$power, "%"), 
                                   paste0("False Difference\n", 100 - input$confidence, "%"),
                                   paste0("False \"No Difference\"\n", 100 - input$power, "%"), 
                                   paste0("True \"No Difference\"\n", input$confidence, "%")),
                         
                         # The min and max coords for the false positive/false negative quadrants
                         rect_max_error = c(0, (100*(100-input$confidence))^0.5, 100,0),
                         rect_min_error = c(0,0, 100 - (100*(100-input$power))^0.5,0),
                         
                         # The min/max for the true positive/true negative quadrants
                         rect_min_good_x = c(100 - (100*input$power)^0.5,0,0,0),
                         rect_min_good_y = c(0,0,0,100 - (100*input$confidence)^0.5),
                         rect_max_good_x = c(100,0,0,(100*input$confidence)^0.5),
                         rect_max_good_y = c((100*input$power)^0.5,0,0,100),
                         
                         # The coin toss rectangle coordinates. Since this is built as facets,
                         # these are actually four static boxes that look like "one box" based
                         # on how they're plotted
                         rect_min_coin_x = c(100 - 5000^0.5,0,100 - 5000^0.5,0),
                         rect_min_coin_y = c(0,0,100 - 5000^0.5,100 - 5000^0.5),
                         rect_max_coin_x = c(100,5000^0.5,100,5000^0.5),
                         rect_max_coin_y = c(5000^0.5,5000^0.5,100,100),
                         
                         # The tooltips used for each rectangle
                         tooltips_error = c("", 
                                            paste0("If there truly is NOT a difference, ",
                                                   100 - input$confidence, "% of the time, the test ",
                                                   "will INCORRECTLY report there IS a difference."), 
                                            paste0("If there truly IS a difference, ",
                                                   100 - input$power, "% of the time, the test ",
                                                   "will INCORRECTLY report there is NOT a difference."), 
                                            ""),
                         tooltips_good = c(paste0("If there truly IS a difference, ",
                                                  input$power, "% of the time, the test ",
                                                  "will (correctly) report there is a difference."),
                                           "", 
                                           "", 
                                           paste0("If there truly is NOT a difference, ",
                                                  input$confidence, "% of the time, the test ",
                                                  "will (correctly) report there is not a difference."))
                         
  )
  
  # Build the plot
  error_gg <- ggplot(data = error_df, mapping = aes(label = label)) +
    
    # Fill in the "Correct Conclusion" quadrants as green
    geom_rect_interactive(aes(xmin = rect_min_good_x, xmax = rect_max_good_x,
                              ymin = rect_min_good_y, ymax = rect_max_good_y,
                              tooltip = tooltips_good),
                          fill = "#B8D8BA") +
    
    # Draw the rectangles that will show how much the risk is
    geom_rect_interactive(aes(xmin = rect_min_error, xmax = rect_max_error,
                              ymin = rect_min_error, ymax = rect_max_error,
                              tooltip = tooltips_error),
                          fill = "#EF959D") +
    
    # Draw the "coin toss" box
    geom_rect(aes(xmin = rect_min_coin_x, xmax = rect_max_coin_x,
                  ymin = rect_min_coin_y, ymax = rect_max_coin_y),
              fill = NA, colour = "gray70", linetype = "dotted", size=1) +
    
    # Draw the axes
    geom_hline(aes(yintercept=c(0,0,100,100)), size=1, colour="gray40") +
    geom_vline(aes(xintercept=c(100,0,100,0)), size=1, colour="gray40") +
    
    # Label the four quadrants
    geom_text(aes(x=50, y=c(50,50,50,50)), size = 5, fontface = "bold") +
    
    # Get rid of padding
    scale_x_continuous(limits = c(0,100), expand = c(0,0), position = "top") +
    scale_y_continuous(limits = c(0,100), expand = c(0,0)) +
    
    # Make the quadrants by way of faceting
    facet_grid(result ~ reality, switch = "y") +
    
    # Add the labels
    labs(x = "Reality (Truth)", y = "Test Result (Challenger vs. Control)") +
    
    # Apply the theme
    error_theme 
  
  # Return the plot. We're using ggiraph for this so that we can use the
  # tooltips. See https://rdrr.io/cran/ggiraph/man/geom_rect_interactive.html and
  # https://stackoverflow.com/questions/40199178/shiny-how-to-use-ggiraph
  ggiraph(code = print(error_gg),
          selection = "none")
})
```

Row
-----------------------------

_This calculator is built with R using the `power.prop.test()` function (for the actual calculations), which performs a two-sample test for proportions. Read more in the [documentation for the function](https://www.rdocumentation.org/packages/stats/versions/3.4.3/topics/power.prop.test)._

<div style="display: none;">
```{r url_bookmarking}
# The code below uses query parameters in the URL of the page so that the total configuration 
# is captured in the URL, enabling someone to "come back" to the exact configuration at any point.
# See details at: https://shiny.rstudio.com/reference/shiny/1.5.0/updateQueryString.html.
# This chunk is wrapped in a <div> that sets the display to none because, otherwise, a little
# bit of JS gets rendered that chunk options are unable to turn off.
enableBookmarking("url")
observe({
  # Trigger this observer every time an input changes
  reactiveValuesToList(input)
  session$doBookmark()
})
onBookmarked(function(url) {
  updateQueryString(url)
})
```
</div>